Total Platform Cyber Protection

### 2016-06-02 paper.tex
finished proof-reading till section 8.2.3, have to start writing 8.2.5

Not all security vulnerabilities are the result of memory corruption
or other programming language-based flaws. Another kind of
vulnerability class are called logic (or implementation) flaws. These
flaws occur when the logic of the application is faulty. Consider an
ecommerce application that allows a coupon to be reapplied to an order
multiple times, driving the price to zero. Or if a user is able to
enter a negative quantity for the purchase of an item, and the
application uses that negative quantity to refund the purchase price!

@@

Other classes such as preventing access control
vulnerabilities~\cite{dalton09:nemesis} or statically detecting
them~\cite{Sun2011}. Privilege escalation
vulnerabilities~\cite{Monshizadeh2014}, data disclosure
vulnerabilities~\cite{Muthukumaran2015}

Parameter tampering vulnerabilities are another type of logic
flaw~\cite{Bisht2010, Bisht2011}

Execution After Redirect are another type of logic flaw
vulnerabilities in web applications~\cite{Doupe2011, Payet2013}

Single sign-on vulnerabilities~\cite{Zhou2014}.

Work on detecting logic vulnerabilities directly started with
attempting to infer security specifications of an
application~\cite{tan08:autoises, Livshits2009a}. Other approaches dynamically
execute the application to infer likely invariants, then static
analysis attempts to find paths that violation those
invariants~\cite{felmetsger10:logic}. Further work tried to find missing
security (authorization) checks automatically, without prior knowledge
of the checks~\cite{Son2011, Son2013}.

Recent work has looked at detecting logic flaw vulnerabilities in web
applications in a black-box manner---that is, no knowledge of the
application's source code~\cite{Pellegrino2014}.

>>>>

Not all security vulnerabilities are the result of memory corruption
or other programming language-based flaws. Another kind of
vulnerability class is called logic (or implementation) flaws. These
flaws occur when the logic of the application is faulty. Consider an
e-commerce application that allows a coupon to be reapplied to an order
multiple times, driving the price to zero. Or if a user is able to
enter a negative quantity for the purchase of an item, and the
application uses that negative quantity to refund the purchase price!

@@

Other research has looked at preventing access control
vulnerabilities~\cite{dalton09:nemesis}, or statically detecting
them~\cite{Sun2011}.
Some research has looked at other types of logic
flaws, such as
Privilege escalation vulnerabilities~\cite{Monshizadeh2014}, data disclosure
vulnerabilities~\cite{Muthukumaran2015}, single sign-on vulnerabilities~\cite{Zhou2014}, and parameter tampering vulnerabilities~\cite{Bisht2010, Bisht2011}.

Execution After Redirect is another type of logic flaw
vulnerability in web applications~\cite{Doupe2011, Payet2013}.

Work on detecting logic vulnerabilities directly started with
attempting to infer security specifications of an
application~\cite{tan08:autoises, Livshits2009a}. Other approaches dynamically
execute the application to infer likely invariants, then use static
analysis to attempt to find paths that violate those
invariants~\cite{felmetsger10:logic}. Further work tried to find missing
security (authorization) checks automatically, without prior knowledge
of the checks~\cite{Son2011, Son2013}.

% citation needed here for black-box testing
Recent work has looked at detecting logic flaw vulnerabilities in web
applications in a black-box manner---that is, with no knowledge of the
application's source code~\cite{Pellegrino2014}.
